\chapter{Problem Statement}
\label{ch:problem-statement}

The problem this project addresses can be stated in a single sentence:

\begin{quote}
Existing navigation systems stop at the entrance of heritage sites, leaving
visitors without guidance to explore monuments, discover historical
significance, or experience Nepal's cultural heritage in a structured and
engaging way.
\end{quote}

\section{The Situation}
Nepal welcomed 1.147 million international tourists in
2024~\cite{nepaltourism2024},
and its heritage sites collectively receive over a million visitors
annually. Consumer navigation applications serve these visitors well up to a
point: they can route anyone to the gate of a temple complex, a museum, or a
university campus. Beyond the gate, however, the visitor is on their own.
Physical tourism centres --- which provide maps, information about places of
interest, and basic visitor services --- have been established in Nepal only
in limited places, a scarcity identified in the literature as a serious
deterrent to the development of tourism in the
country~\cite{nepaltourismchallenges}.
The same pattern holds at a smaller scale on educational campuses, where
newcomers face unfamiliar geography with no structured way to explore it.

\section{The Specific Gap}
Once inside a site, four things are missing.

\begin{enumerate}
  \item \textbf{No structured navigation.} There is no guided route through
        the premises; visitors wander, miss significant locations, and have
        no sense of a complete journey.
  \item \textbf{No contextual storytelling.} The history and significance of
        each monument or location is not delivered at the place itself,
        where it would be most meaningful.
  \item \textbf{No engagement incentive.} Nothing rewards deeper
        exploration, revisits, or learning; the visit is passive.
  \item \textbf{No verification of presence.} Institutions have no way to
        confirm that a visitor actually stood at a location, which rules out
        trustworthy completion records, rewards, or engagement analytics.
\end{enumerate}

This gap is not merely anecdotal. UNESCO recommends that every heritage site
provide visitors with easily accessible information --- maps, navigation, and
cultural interpretation --- through a centralised platform, while observing
that surprisingly few World Heritage sites actually provide such accessible
digital
resources~\cite{unescotoolkit}.
UN Tourism likewise emphasises that digital technologies play a vital role
in improving cultural tourism by modernising heritage interpretation,
increasing visitor engagement, and delivering innovative educational
experiences~\cite{unwto2018}.

\section{Why Existing Approaches Fall Short}
The traditional answer to the guidance gap is the human-guided tour --- the
campus orientation walk or the hired heritage guide. This model has four
structural weaknesses:

\begin{itemize}
  \item \textbf{Passive and forgettable.} A guide speaks, the audience
        listens, and little is retained.
  \item \textbf{Non-scalable.} Every tour requires a human guide and cannot
        run simultaneously for hundreds of newcomers.
  \item \textbf{Zero data.} Institutions gain no insight into which
        locations visitors actually engage with.
  \item \textbf{One-and-done.} There is no replay value and no incentive to
        revisit.
\end{itemize}

A number of digital alternatives exist in Nepal --- curated guide
applications, archival heritage databases, self-guided GPS tour products,
and QR-coded storyboards installed at sites --- but none combines real-time
wayfinding with AR presentation, presence verification, and gamified
engagement, and some depend on physical hardware installed and maintained at
every location. A detailed comparison of these competitors is given in
Chapter~\ref{ch:market-analysis}.

\section{Consequence of Leaving It Unsolved}
If the gap remains open, the cost is borne on all sides. Visitors leave
heritage sites having seen stone and brick but not the stories that give
them meaning; students finish orientation without ever genuinely learning
their campus. Institutions continue to pay for guided tours that do not
scale and produce no data, and they miss the engagement and educational
outcomes that international tourism bodies explicitly identify as the value
of digital interpretation. For Nepal in particular --- a country whose
tourism sector depends heavily on its cultural heritage --- every
undirected, unengaged visit is an opportunity lost.

\section{Motivation}
Two developments make this problem solvable now rather than at some future
date. First, smartphones are ubiquitous among both tourists and students,
and each one already carries the required hardware: a GPS receiver, a
magnetometer, and a camera. Second, browser platform APIs for geolocation,
device orientation, and camera access have matured to the point where
location-based AR runs directly in a mobile web page, with no application
store, no installation step, and no physical infrastructure at the site.
A solution can therefore be deployed to any premises purely as software.

The project deliberately starts with a campus as its proving ground. A
campus is a controlled premises: routes are short, waypoints are known,
users are reachable for feedback, and the complete loop --- geofenced
navigation, AR media, gamification, and admin tooling --- can be validated
end-to-end within the hackathon timeframe. Once proven at Orchid College,
the same configurable platform can be pointed at heritage sites such as
Pashupatinath, Boudhanath, or any of Nepal's ten UNESCO World Heritage
properties without changes to the codebase.
