\chapter{Market Context}
\label{ch:market-analysis}
% Condensed summary of docs/02_market_analysis.md

\section{Target Users}
\projectname{} serves three user groups. \textbf{Students and campus
newcomers} are the primary segment: orientation is chaotic, campus geography
is unfamiliar, and nothing incentivises exploration; the platform gives them
a self-guided AR tour with badges, a peer leaderboard, and tangible perks.
\textbf{Heritage-site visitors}, domestic and international, form the
secondary segment: guides are scarce and cultural context is inaccessible on
site; the platform provides a GPS-guided route with story media at each
monument and a quiz to reinforce learning. \textbf{Site administrators and
institutions} are the tertiary segment: guided tours cost staff time, produce
no data, and end after orientation day; the platform replaces them with a
zero-hardware digital experience and visitor-count analytics.

\section{Why Nepal}
Nepal received 1.147 million international tourists in
2024~\cite{nepaltourism2024},
holds ten UNESCO World Heritage properties (four cultural sites in the
Kathmandu Valley alone)~\cite{unesconepal},
and derives roughly 7--8\,\% of GDP from tourism. Physical tourism centres
are scarce, and UNESCO explicitly observes that few World Heritage sites
provide accessible digital visitor resources. The market therefore combines
a large addressable audience with a documented absence of digital
infrastructure.

\section{Existing Solutions}
Table~\ref{tab:competitors} summarises the Nepal-specific alternatives. None
combines real-time wayfinding, AR presentation, presence verification, and
gamified engagement; one (Saarang) additionally depends on physical QR
boards installed and maintained at every site.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}p{0.24\textwidth}p{0.36\textwidth}p{0.32\textwidth}@{}}
    \toprule
    \textbf{Solution} & \textbf{Mechanic} & \textbf{Gap} \\
    \midrule
    HoneyGuide Nepal & Curated cultural walking guides & No AR, no navigation loop, no gamification \\
    Nepal Heritage App & Archival site documentation & Database, not a guided journey \\
    GPSmyCity & Generic self-guided GPS city tours & No AR, no engagement mechanics, city-scale only \\
    Kathmandu Durbar App & Paid GPS walking-tour product & Single product, no platform or admin tooling \\
    Lokalee & Digital concierge with one heritage trail & Tours are peripheral to a booking app \\
    Saarang & QR storyboards installed at sites & Physical hardware per site; no navigation \\
    \bottomrule
  \end{tabular}
  \caption{Nepal-specific competitive landscape.}
  \label{tab:competitors}
\end{table}

\section{Differentiation}
\projectname{} addresses every gap in Table~\ref{tab:competitors} at once:
browser-based location AR with zero physical installation, a live wayfinding
loop over WebSocket, geofence-verified presence, a full gamification layer
(points, badges, quizzes, side quests, redemption), and an admin GUI with
which any institution can configure a new route in minutes. The campus focus
is itself a differentiator: the listed competitors target city-scale tourism
and leave controlled premises such as campuses and museums unserved.
