\chapter{Design Process}
\label{ch:design-thinking}
% Condensed summary of docs/03_design_thinking.md

The product was shaped by one pass through the Stanford d.school
design-thinking cycle (empathise, define, ideate, prototype, test). This
chapter summarises the decisions that survived into the build.

\section{Research and Definition}
Empathy work combined informal interviews with eight first-year students at
Orchid College, observation of a standard orientation day, a review of campus
group chats for recurring lost/confused messages, and desk research on Nepal
tourism. Recurring findings: students still could not locate basic facilities
months after orientation (``I still don't know where the parking area is
after 3 months''); the guided tour moved too fast to retain; staff spent
3+ hours per orientation day on tour logistics; and the campus's history had
no accessible presentation. The problem was framed as: how might we create a
heritage and campus exploration experience that is self-directed, GPS-guided,
and story-rich, so that visitors feel oriented and engaged while institutions
gain digital visibility with zero hardware.

Three personas guided prioritisation: a first-year student who needs fast
orientation and a sense of belonging; an orientation coordinator who needs to
reduce manual effort and obtain engagement data without being a developer;
and a competitive second-year student motivated by badges, points, and
rankings.

\section{Selected and Rejected Ideas}
Ideation converged on GPS-anchored AR overlays, story videos at milestones,
physical reward redemption, post-route quizzes, optional side quests, a
community page, and an admin waypoint logger --- all shipped. Rejected for
feasibility or scope: real-time multiplayer racing, QR-code check-ins (no AR
value), and creature-collection mechanics. The product was built as a web
application rather than a native app so that users enter through a URL with
no installation, one codebase covers Android and iOS browsers, and admins use
the same origin with role-based routing.

\section{Validation During the Build}
Field testing directly changed the design, as summarised in
Table~\ref{tab:validation}.

\begin{table}[h]
  \centering\small
  \begin{tabular}{@{}p{0.42\textwidth}p{0.50\textwidth}@{}}
    \toprule
    \textbf{Observation} & \textbf{Design response} \\
    \midrule
    5\,m arrival threshold too tight; users could not trigger arrival & Default geofence raised to 10\,m and made admin-configurable per place \\
    AR video autoplay blocked on iOS & Tap-to-play fallback overlay \\
    Compass inert on first launch (iOS) & Explicit \code{DeviceOrientationEvent} permission gate behind a user gesture \\
    Quiz felt like a chore after a walk & Capped at five questions; answer-review mode added after the single attempt \\
    Redemption page hard to discover & AR-points balance surfaced on the dashboard header \\
    Indoor demos impossible without GPS & Full demo mode with simulated arrivals \\
    \bottomrule
  \end{tabular}
  \caption{Field observations and the design responses they produced.}
  \label{tab:validation}
\end{table}
