\chapter{Gamification Engine}
\label{ch:gamification}
% Port from: docs/09_gamification_engine.md

The gamification layer converts physical exploration into a tracked game
loop built from four interlocking systems: AR~Points, milestones and badges,
side quests, and quizzes. All rewards are persistent (they survive progress
resets) and idempotent (repeating an action cannot duplicate a reward).

\section{AR Points}
AR~Points are a private virtual currency. The balance appears only on the
owner's dashboard and redemption page; it is never included in public
profiles, the people directory, or the leaderboard. Table~\ref{tab:points}
lists the earning rules. On the seeded Orchid College route the theoretical
maximum is 100 points: two milestones (20), one side quest (25), place
completion (20), and a perfect quiz (35).

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llr@{}}
    \toprule
    \textbf{Action} & \textbf{Ledger source} & \textbf{Points} \\
    \midrule
    Visiting a milestone waypoint & \code{milestone} & 10 \\
    Completing a side quest (5-minute stay) & \code{side\_quest} & 25 \\
    Completing every checkpoint of a place & \code{place\_complete} & 20 \\
    Quiz: 1 / 2 / 3 / 4 / 5 of 5 correct & \code{quiz} & 10 / 20 / 25 / 30 / 35 \\
    Redemption & \code{redeem} & negative (cost) \\
    \bottomrule
  \end{tabular}
  \caption{AR~Points earning and spending rules.}
  \label{tab:points}
\end{table}

Awards are idempotent by construction: each carries a
\code{(source, ref\_id)} key and the ledger rejects duplicates (see the
listing in Appendix~\ref{app:code}), so GPS glitches, re-confirmations, and
revisits cannot farm points.

\section{Milestones and Badges}
A milestone is a waypoint whose arrival plays a narrative video; confirming
it awards points and appends the milestone permanently to the user's
profile. A badge is a place-level award, granted when all of a place's
milestone checkpoints are complete (for places without milestones, when the
full route is complete). Because badge computation consults the permanent
records --- profile milestones and the place-completion ledger entry --- as
well as live progress, badges survive progress resets: a user who revisits
a place walks a fresh route but keeps every earned badge.

\section{Side Quests}
A side quest is an optional detour. On arrival its video plays, after which
the user may accept or skip. Accepting starts a five-minute countdown during
which the user must remain on site; only when the timer completes is the
checkpoint confirmed and the 25-point award made. The dwell requirement
ensures the reward reflects genuine engagement with the location rather
than a tap-and-leave.

\section{Quizzes}
Each place may carry exactly one quiz of five multiple-choice questions.
Three rules shape the experience: the quiz is \emph{locked} until the user
has completed every checkpoint of the place; each user gets exactly
\emph{one attempt}, ever; and correct answers are \emph{stripped} from all
API responses to regular users until that attempt is spent. After
submission the user sees a scored review --- each question with the correct
option and their own pick marked --- and the entry point changes from
``Give quiz'' to ``View quiz answers''.

\section{Redemption}
Points are spent on tangible campus perks defined in a server-side catalog
(Table~\ref{tab:rewards}). Redemption checks the balance, appends a
negative ledger entry, and decrements the total; fulfilment is manual (the
student shows the confirmation to staff). Unlike awards, redemptions may
repeat, so each receives a unique ledger reference.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llr@{}}
    \toprule
    \textbf{Reward} & \textbf{Description} & \textbf{Cost} \\
    \midrule
    Canteen tea voucher & A free cup of tea at the campus canteen & 30 \\
    Orchid sticker pack & Limited-edition campus stickers & 60 \\
    Table tennis session & 30 minutes at the table tennis table & 90 \\
    Orchid T-shirt & An official Orchid College tee & 250 \\
    \bottomrule
  \end{tabular}
  \caption{Rewards catalog.}
  \label{tab:rewards}
\end{table}

\section{Leaderboard and Community}
The people section shows a community leaderboard by default, replaced live
by search results as the user types (input debounced at 300\,ms). It ranks
active users by a chosen public metric --- milestones, places visited, or
side quests completed --- with stable tie-breaking across the other two.
AR~Points are deliberately excluded from the ranking and from public
profiles: the competitive surface uses only observable exploration facts,
while the currency stays private to its owner.
